---
title: "MAET Technology Survey - Results"
author: "Joshua Rosenberg"
date: "10/14/2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Just comparing pre-post survey results

```{r, eval = F, echo = F}
# library(googlesheets)
library(readxl)
library(tidyverse)

df1 <- read_xlsx('Surveys/MAET 2013 Tech Survey (Responses).xlsx')
#df1 <- gs_read(df1, ws = 1)

df2 <- read_xlsx('Surveys/MAET 2014 Tech Pre-Survey (Responses) x.xlsx')
#df2 <- gs_read(df2, ws = 1)

df3 <- read_xlsx('Surveys/MAET 2015 Tech Pre-Survey (Responses).xlsx')
#df3 <- gs_read(df3, ws = 1)
#df3

df4 <- read_xlsx('Surveys/MAET 2016 Tech Pre-Survey (Responses).xlsx')
#df4 <- gs_read(df4, ws = 1)
df4 <- select(df4, -54, -53, -52, -51)
#df4

df5 <- read_xlsx('Surveys/MAET 2017 Tech Pre-Survey (Responses).xlsx')
#df5 <- gs_read(df5, ws = 1)
df5 <- select(df5, -52, -51)
#df5

nrow(df1) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5)

names_df <- data_frame(names_df1 = names(df1),
                       names_df2 = names(df2),
                       names_df3 = names(df3),
                       names_df4 = names(df4),
                       names_df5 = names(df5))

names_df # checking these are all named the same

names(df1) <- names(df5)
names(df2) <- names(df5)
names(df3) <- names(df5)
names(df4) <- names(df5)
names(df5) <- names(df5)

df_pre <- bind_rows(df1, df2, df3, df4, df5) # 74 observations from five years

df_pre <- mutate(df_pre, 
                 date = lubridate::mdy_hms(Timestamp),
                 year = lubridate::year(date), 
                 time = "pre")

# Posts

df1 <- read_xlsx('Surveys/MAET 2013 Tech Post-survey  (Responses).xlsx')
# df1 <- gs_read(df1, ws = 1)
# df1

df2 <- read_xlsx('surveys/MAET 2014 Tech Post-Survey  (Responses).xlsx')
#df2 <- gs_read(df2, ws = 1)

df3 <- read_xlsx('surveys/MAET 2015 Tech Post-Survey  (Responses).xlsx')
# df3 <- gs_read(df3, ws = 1)
# df3

df4<- read_xlsx('surveys/MAET 2016 Tech Post-Survey (Responses).xlsx')
#df4 <- gs_read(df4, ws = 1)
df4 <- select(df4, -54, -53, -52, -51)
#df4

df5 <- read_xlsx('surveys/MAET 2017 Tech Post-Survey (Responses).xlsx')
#df5 <- gs_read(df5, ws = 1)
df5 <- select(df5, -54, -53, -52, -51)
#df5

# sd <- read_xlsx('surveys/Summary Data MAET Survey.xlsx')
#sd <- gs_read(sd, ws = 1)

nrow(df1) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) # 69 post obs 

names_df <- data_frame(names_df1 = names(df1),
                       names_df2 = names(df2),
                       names_df3 = names(df3),
                       names_df4 = names(df4),
                       names_df5 = names(df5))

names_df # checking these are named the same

names(df1) <- names(df5)
names(df2) <- names(df5)
names(df3) <- names(df5)
names(df4) <- names(df5)
names(df5) <- names(df5)

df_post <- bind_rows(df1, df2, df3, df4, df5)
df_pre <- rename(df_pre, "Most Important" = "Want to Learn More")

df_post <- mutate(df_post, 
                  date = lubridate::mdy_hms(Timestamp),
                  year = lubridate::year(date), 
                  time = "post")

# All

# b <- gs_title('Summary Data MAET Survey')
# b <- gs_read(b, ws = 1)
# the_cat <- as.numeric(as.vector(unlist(b[b$Timestamp == "Type of variable", ])))
# the_cat

d <- bind_rows(df_pre, df_post)
#write_csv(d, "2017-10-27-MAET-tech-survey-all-data.csv")
#write_csv(sd, "data-with-cats.csv")
```

Loading data

```{r, message = F, warning = F, eval = FALSE}
library(googlesheets)
library(tidyverse)
d <- read_csv('maet-survey.csv', col_types = cols(
  .default = col_double(),
  Timestamp = col_character(),
  `Want to Learn More` = col_character(),
  date = col_datetime(format = ""),
  time = col_character()
))

d <- slice(d, 2:nrow(d))

dd <- read_csv('maet-survey.csv')
sd <- slice(dd, 1:1)
#key <- slice(d, 1:1)
#d <- read_csv("2017-10-27-MAET-tech-survey-all-data.csv")
#sd <- read_csv("2017-10-27-MAET-tech-survey-key.csv")
```

With all variables - test

```{r}
oo <- data.frame()

for (i in 3:49){
    x <- as.vector(unlist(d[, i]))
    y <- as.vector(d$time)
    o <- t.test(x ~ y, paired = F)
    to <- broom::tidy(o)
    cd <- effsize::cohen.d(x, y, paired=F)
    to$cohen_d <- abs(cd$estimate)
    oo <- bind_rows(oo, to)
    oo <- as_tibble(oo)
}

oo$var <- names(d)[3:49]
oo <- select(oo, var, pre = estimate2, post = estimate1, diff = estimate, t_statistic = statistic, p_value = p.value,  cohen_d)
oo$p_value <- round(oo$p_value, 3)
clipr::write_clip(oo)
```

With all variables - plot

```{r}
calc_se <- function(x) {
    sd(x, na.rm = T) / sqrt(length(x) -1)
}

x <- d %>%
    group_by(time) %>% 
    summarize_at(.vars = vars(`Overall Confidence`:`Navigate a Firewall`), funs(mean, calc_se)) %>% 
    gather(key, val, -time) %>% 
    mutate(type = str_detect(key, "calc_se")*1,
           type = if_else(type == 0, "mean", "se")) %>% 
    group_by(key) %>% 
    spread(type, val)

y <- c(x$mean[-1], NA)

x$mean <- y

x <- filter(x, !is.na(mean))
x <- ungroup(x)  
x <- mutate(x, key = str_sub(key, end = -9))

tm <- sd %>% 
    filter(Timestamp == "Type of variable") %>% 
    gather(key, val) %>% 
    mutate(nval = as.integer(val)) %>% 
    filter(!is.na(nval) & !is.na(val)) %>% 
    dplyr::select(key, var_type = val) %>% 
    mutate(var_type = ifelse(var_type == 1, "Low",
                             ifelse(var_type == 2, "Medium", "High")),
           var_type = forcats::fct_relevel(var_type, (c("Low", "Medium", "High"))))

x %>% 
    left_join(tm) %>% 
    filter(!is.na(var_type)) %>% 
    mutate(time = forcats::fct_relevel(as.factor(time), c("pre", "post"))) %>% 
    ggplot(aes(x = reorder(key, mean), y = mean, ymin = (mean-(1.96*se)), ymax = (mean + (1.96*se)), linetype = time, color = var_type)) +
    geom_point(position = position_dodge(width = 1)) +
    geom_errorbar(position = position_dodge(width = 1)) +
    coord_flip() +
    xlab(NULL) +
    ylab("Mean Score") + 
    scale_color_brewer("Alignment", type = "qual", palette = 2) +
    theme_bw() +
    scale_linetype_manual("Survey Timepoint", labels = c("Pre-class", "Post-class"), values = c("dashed", "solid"))

# x %>%
#     left_join(tm) %>%
#     filter(!is.na(var_type)) %>%
#     ggplot(aes(x = reorder(key, mean), y = mean, fill = time, ymin = (mean-(1.96*se)), ymax = (mean + (1.96*se)))) +
#     facet_wrap(~var_type, ncol = 1, scales = "free") +
#     geom_col(position = "dodge") +
#     geom_errorbar(position = "dodge") +
#     coord_flip() +
#     xlab(NULL) +
#     ylab("Value") +
#     scale_fill_discrete("Survey Timepoint", labels = c("Pre-class", "Post-class")) +
#     theme_bw() +
#     theme(legend.position="bottom", text = element_text(size = 13)) +
#     theme_bw()
# 
# x %>%
#     left_join(tm) %>%
#     filter(!is.na(var_type)) %>%
#     ggplot(aes(x = reorder(key, mean), y = mean, fill = time, ymin = (mean-(1.96*se)), ymax = (mean + (1.96*se)))) +
#     geom_col(position = "dodge") +
#     geom_errorbar(position = "dodge") +
#     geom_point(position = "dodge") +
#     coord_flip() +
#     xlab(NULL) +
#     ylab("Value") +
#     scale_fill_discrete("Survey Timepoint", labels = c("Pre-class", "Post-class")) +
#     theme_bw() +
#     theme(legend.position="bottom", text = element_text(size = 13)) +
#     theme_bw()
```

```{r}
ddd <- d %>% select(`Syncing Email`:`Navigate a Firewall`) %>% gather(key, val) %>% left_join(tm)

r1 <- ddd %>% # 26
  filter(var_type=="Low") %>% 
  group_by(key) %>% 
  mutate(row_n = row_number()) %>% 
  spread(key, val) %>% 
  select(-var_type, -row_n)

psych::alpha(as.matrix(r1)) # 0.92

r2 <- ddd %>% # 12
  filter(var_type=="Medium") %>% 
  group_by(key) %>% 
  mutate(row_n = row_number()) %>% 
  spread(key, val) %>% 
  select(-var_type, -row_n)

psych::alpha(as.matrix(r2)) # 0.88

r3 <- ddd %>% # 8 
  filter(var_type=="High") %>% 
  group_by(key) %>% 
  mutate(row_n = row_number()) %>% 
  spread(key, val) %>% 
  select(-var_type, -row_n)

psych::alpha(as.matrix(r3)) # 0.83
```

```{r}
t <- read_csv("t-tests.csv")
t <- slice(t, 1:47)
t$adjusted_p_value <- p.adjust(t$p_value, method = "hochberg")
```

By grouping variables

Variable definitions:

* Overall: represents overall confidence and overall confidence for teaching and learning

* 1: represents don't do it / haven't done it over the past five years
* 2: represents may do it / have possibly done it over the past five years
* 3: represents definitely do it / have used it over the past five years

```{r}
x <- sd[1, ] %>% 
    select(-Timestamp, -date, -year, -`Want to Learn More`) %>% 
    gather(key, var_type, -time) %>% 
    mutate(var_type = case_when(
        var_type == "Overall" ~ "Overall",
        var_type == 1 ~ "Low Alignment",
        var_type == 2 ~ "Medium Alignment",
        var_type == 3 ~ "High Alignment"
    ))

nd <- names(d)[3:49]

ta <- d %>%
    select(-Timestamp, -date, -year, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    rename(time = time.x) %>% 
    select(-time.y) %>% 
    filter(var_type != "Overall")

m1 <- lm(val ~ var_type*time, data = ta)
summary(m1)

m1i <- aov(val ~ var_type*time, data = ta)
summary(m1i)
TukeyHSD(m1i)

ta <- d %>%
    select(-Timestamp, -date, -year, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    rename(time = time.x) %>% 
    select(-time.y) %>% 
    filter(time == "pre")

r <- aov(ta$val ~ ta$var_type)
summary(r)
TukeyHSD(r)

ta <- d %>%
    select(-Timestamp, -date, -year, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    rename(time = time.x) %>% 
    select(-time.y) %>% 
    filter(time == "post")

m1 <- lm(val ~ var_type*time, data = ta)

r <- aov(ta$val ~ ta$var_type)
summary(r)
TukeyHSD(r)

p <- d %>%
    select(-Timestamp, -date, -year, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    rename(time = time.x) %>% 
    group_by(time, var_type) %>% 
    mutate(val= as.numeric(val)) %>% 
    summarize(mean_val = mean(val, na.rm = T),
              se_val = calc_se(val)) %>% 
    ungroup() %>% 
    mutate(var_type = forcats::fct_relevel(var_type,
                                           c("Low Alignment", "Medium Alignment", "High Alignment", "Overall")),
           time = forcats::fct_relevel(time, c("pre", "post"))
    )

ggplot(p, aes(x = var_type, y = mean_val, fill = time, ymin = (mean_val-(1.96*se_val)), ymax = (mean_val + (1.96*se_val)))) +
    geom_col(position = "dodge") +
    geom_errorbar(position = "dodge") +
    xlab(NULL) +
    ylab("Value") +
    scale_fill_discrete("Survey Timepoint", labels = c("Pre-class", "Post-class")) +
    theme_bw() +
    geom_vline(xintercept = 3.5, linetype = "dashed") +
    theme(text = element_text(family = "Times", size = 14)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("overall-diff.png", width = 8, height = 5)
```

```{r}
d %>% 
    select(-Timestamp, -year, -date, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    select(time = time.x, everything(), -time.y) %>% 
    filter(var_type == "Overall") %>% 
    tidyttest::t_test(val, time)

d %>% 
    select(-Timestamp, -year, -date, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    select(time = time.x, everything(), -time.y) %>% 
    filter(var_type == "Low Alignment") %>% 
    tidyttest::t_test(val, time)

d %>% 
    select(-Timestamp, -year, -date, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    select(time = time.x, everything(), -time.y) %>% 
    filter(var_type == "Medium Alignment") %>% 
    tidyttest::t_test(val, time)

x <- d %>% 
    select(-Timestamp, -year, -date, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    select(time = time.x, everything(), -time.y) %>% 
    filter(var_type == "High Alignment") %>% 
    t_test_test()
```

```{r}
d %>%
    select(-Timestamp, -date, -year, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>%
    rename(time = time.x)
```


```{r, t-test-fun}
t_test_test <- function(df, dv, group) {
    
    dv_q <- as.character(substitute(dv))
    group_q <- as.character(substitute(group))
    
    dv_enquo <- dplyr::enquo(dv)
    group_enquo <- dplyr::enquo(group)
    
    the_formula <- stats::as.formula(paste(dv_q, " ~ ", group_q))
    test_results <- stats::t.test(the_formula, data = df)
    
    print(paste(names(test_results$estimate[1]), " is ", round(test_results$estimate[1], 3)))
    print(paste(names(test_results$estimate[2]), " is ", round(test_results$estimate[2], 3)))
    
    print(paste("Test statistic is ", round(test_results$statistic, 3)))
    print(paste("P-value is ", round(test_results$p.value, 3)))
    
    the_ns <- dplyr::count(df, !! group_enquo)
    the_ns <- dplyr::pull(the_ns, n)
    
    effect_size_results <- compute.es::tes(test_results$statistic,
                                           n.1 = the_ns[1],
                                           n.2 = the_ns[2],
                                           verbose = F)
    
    print(paste("Effect size is ", effect_size_results$d))
    
    #broom::tidy(test_results)
    out <- dplyr::data_frame(group_1_mean = round(test_results$estimate[1], 3),
                             group_2_mean = round(test_results$estimate[2], 3),
                             test_statistic = round(test_results$statistic, 3),
                             p_value = round(test_results$p.value, 3),
                             effect_size = effect_size_results$d)
    
    invisible(out)
    
}
```

```{r}
d %>% 
    select(-Timestamp, -year, -date, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    select(time = time.x, everything(), -time.y) 

d %>% 
    select(-Timestamp, -year, -date, -`Most Important`) %>% 
    gather(key, val, -time) %>% 
    left_join(x, by = "key") %>% 
    select(time = time.x, everything(), -time.y) %>% 
    filter(var_type == "High Alignment")
    
```